---
title: "CS549 Assignment#4"
author: "Mohamed_Shibl"
date: "Sep 25, 2016"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Obtaining R_Squared
Running a multiple linear regression example with a model where Y = Ozone, X1 = Temp, X2 = Wind.
This equation will provide us with the value of R_squared.

In this case R_squared is equal 0.5814. Which is a relatively low value meaning that knowing the value of wind and tempreature does not provide us with a certain value of ozone.

```{r}
# sets the working directory
setwd("/Users/Shibl/Google Drive/Herguan University/2016 Fall/CS549 - Big Data Analytics/CS549 Assignments/Assignment1_ozone_data")
# Reads the data into R 
mydata<-read.csv("Ozone_data.csv")
# Runs a Regression model and gives the summary output
summary(lm(Ozone ~ Temp+Wind, data = mydata))
```


## Calculating Correlation
Running the code below, will provide us with the correlation between each 2 columns from our data.
Judgung by the numbers produced, we can see that there is a strong negative correlation between Ozone & Wind (-0.612496576). We can also see that there a strong positive correlation between Ozone and Temp (0.698541410)

```{r}
# draws a correlation plot
pairs(mydata)
# calculates the Pearson's correlation coefficient 
cor(mydata)
```

## Calculating Confidence Interval
Running the code below, will provide us with the value of the Ozone with a confidince of 95%.
The values generated from this equation should be within a reasonable range in order for the data to be useful.

```{r}
model1=lm(Ozone ~ Temp+Wind+Temp*Wind, data = mydata)
confint(model1,conf.level=0.95)
```

## Determining the Statistical Inference of population
Running the code below, will tell us if the sample used in our calculations is considered a fair represntative of the whole population.

```{r}
t.test(mydata,conf.level=0.90)
```

## Hypothesis Testing
Running the code below we test our hypothesis about the data provided, we must provide a null hypothesis and an alternative hypotheis. We will try to disprove the null hypothesis.

After running the code below we can see that we reject the null hypothesis, because the value of p=0.006919 is less than 50.

```{r}
# just separating Ozone data from the data sheet
newdata <- mydata[c(1)]
# Applying T test
t.test(newdata,alternative = "less", mu= 50)
```
